Management induced changes of soil organic carbon on global croplands

### 2020-10-06 ResultNotebooks/results_SOCcompare.Rmd
Mayor update of everything

rev       <- "rev0.6_mrSOC"
outputdir <- "Output/Images"

setConfig(cachefolder  = paste0("/home/kristine/mnt/rd3mod/inputdata/cache/", rev), forcecache = TRUE)
setConfig(sourcefolder = "/home/kristine/mnt/rd3mod/inputdata/sources/")
setConfig(outputfolder = "/home/kristine/mnt/rd3mod/inputdata/output/")
untar(paste0(getConfig("outputfolder"),"/",rev, "_h12_carbonbudget.tgz"), exdir="Data", extras="--keep-newer-files ")

SoilCarbon <- read.magpie("Data/SoilCarbon.rds")
Landuse    <- read.magpie("Data/Landuse.rds")

@@

print(mbind(dimSums(dimSums(SoilCarbon[,,"actualstate"], dim=3.3)* Landuse, dim=c(1,3)),
            dimSums(dimSums(SoilCarbon[,,"steadystate"], dim=3.3)* Landuse, dim=c(1,3))))

@@

  LPJ_IPCC   <- calcOutput("ValidCarbonStocks", datasource = "LPJ_IPCC2006", aggregate="REG+GLO", try=TRUE)
  LPJ_rev21  <- calcOutput("ValidCarbonStocks", datasource = "LPJmL_rev21", aggregate="REG+GLO", try=TRUE)
  LPJ_car    <- calcOutput("ValidCarbonStocks", datasource = "LPJmLCarbon", aggregate="REG+GLO", try=TRUE)
  WISE       <- calcOutput("ValidCarbonStocks", datasource = "WISE", aggregate="REG+GLO", try=TRUE)
  GSOC       <- calcOutput("ValidCarbonStocks", datasource = "GSOC", aggregate="REG+GLO", try=TRUE)
  SoilGrids  <- calcOutput("ValidCarbonStocks", datasource = "SoilGrids", aggregate="REG+GLO", try=TRUE)

@@

plot(c(getYears(glo_SOCStock, as.integer=TRUE)), glo_SOCStock, type="l", col="red", xlim=c(1951,2017),  ylim=c(400000,1300000))
lines(getYears(LPJ_IPCC, as.integer = TRUE), LPJ_IPCC["GLO",,1], type="l", col="green")
lines(getYears(LPJ_car, as.integer = TRUE), LPJ_car["GLO",,], type="l", col="darkgreen")
lines(getYears(LPJ_rev21, as.integer = TRUE), LPJ_rev21["GLO",,2], type="l", col="lightgreen")
lines(getYears(WISE, as.integer = TRUE), WISE["GLO",,], type="l", col="brown")
lines(getYears(SoilGrids, as.integer = TRUE), SoilGrids["GLO",,], type="l", col="blue")
lines(getYears(GSOC, as.integer = TRUE), GSOC["GLO",,], type="l", col="pink")
plot(c(getYears(glo_SOCStock, as.integer=TRUE)), glo_SOCStock, type="l", col="red")
```

>>>>

rev       <- "rev0.76baseline"
outputdir <- "Output/"

setConfig(cachefolder  = paste0("/home/kristine/mnt/rd3mod/inputdata/cache/", rev), forcecache = TRUE)
setConfig(sourcefolder = "/home/kristine/mnt/rd3mod/inputdata/sources/")
setConfig(outputfolder = "/home/kristine/mnt/rd3mod/inputdata/output/")
#untar(paste0(getConfig("outputfolder"),"/",rev, "_h12_carbonbudget.tgz"), exdir="Data", extras="--keep-newer-files ")

SoilCarbon <- read.magpie("Data/Baseline/SoilCarbon.rds")
Landuse    <- read.magpie("Data/Baseline/Landuse.rds")

@@

print(dimSums(dimSums(SoilCarbon[,,"actualstate"], dim=3.3)* Landuse, dim=c(1,3)))

@@

  LPJ_IPCC   <- calcOutput("ValidCarbonStocks", datasource = "LPJ_IPCC2006", aggregate="REG+GLO", try=TRUE)
  #LPJ_rev21  <- calcOutput("ValidCarbonStocks", datasource = "LPJmL_rev21", aggregate="REG+GLO", try=TRUE)
  #LPJ_car    <- calcOutput("ValidCarbonStocks", datasource = "LPJmLCarbon", aggregate="REG+GLO", try=TRUE)
  WISE       <- calcOutput("ValidCarbonStocks", datasource = "WISE", aggregate="REG+GLO", try=TRUE)
  GSOC       <- calcOutput("ValidCarbonStocks", datasource = "GSOC", aggregate="REG+GLO", try=TRUE)
  SoilGrids  <- calcOutput("ValidCarbonStocks", datasource = "SoilGrids", aggregate="REG+GLO", try=TRUE)
  LPJmL4  <- calcOutput("ValidCarbonStocks", datasource = "LPJmL4Paper", aggregate="REG+GLO", try=TRUE)

@@

plot(c(getYears(glo_SOCStock, as.integer=TRUE)), glo_SOCStock, type="l", col="red", xlim=c(1951,2017),  ylim=c(350000,1300000))
lines(getYears(LPJ_IPCC, as.integer = TRUE), LPJ_IPCC["GLO",,1], type="l", col="green")
#lines(getYears(LPJ_car, as.integer = TRUE), LPJ_car["GLO",,], type="l", col="darkgreen")
lines(getYears(LPJmL4, as.integer = TRUE), LPJmL4["GLO",,], type="l", col="lightgreen")
lines(getYears(WISE, as.integer = TRUE), WISE["GLO",,], type="l", col="brown")
lines(getYears(SoilGrids, as.integer = TRUE), SoilGrids["GLO",,], type="l", col="blue")
lines(getYears(GSOC, as.integer = TRUE), GSOC["GLO",,], type="l", col="pink")
plot(c(getYears(glo_SOCStock, as.integer=TRUE)), glo_SOCStock, type="l", col="red")
```

```{r table ipcc scf}

library(knitr)
library(stats)
library(luplot)
library(reshape2)

SOCStock <- mbind(glo_SOCStock, reg_SOCStock)
glo_SOC  <- mbind(setNames(SOCStock[,"y2010",],"SOC Budget"), 
                  setNames(LPJmL4[,"y2010",], "LPJmL4Paper"),
                  setYears(setNames(WISE[,1,],"WISE"), "y2010"),
                  setYears(setNames(SoilGrids[,1,],"SoilGrids"),"y2010"),
                  setYears(setNames(GSOC[,1,],"GSOC"),"y2010"))

#print(dimOrder(comparison[,,sort(getNames(comparison,dim=1))], c(2,1)))

comparison_table  <- data.frame(dcast(as.data.frame(collapseNames(glo_SOC/1000)), 
                           Data1 ~ Region, value.var="Value", 
                            row.names=levels(as.data.frame(glo_SOC)$Data1)))

saveRDS(list(comparison_table = comparison_table), paste0(outputdir,"gloSOC_comparison.rds"))

```{r kable2image}
library(kableExtra)

table <- readRDS("Output/gloSOC_comparison.rds")
colnames(table[[1]])[1] <- "Model/Database"
colnames(table[[1]])[5] <- "Global SOC in GtC"
save_kable(kable_styling(kable(table$comparison_table[c(1,5)], "latex", digit=2), latex_options = c("striped", "scale_down")), 
         file="Output/Images/TableSOC_comparison.png")

save_kable(kable_styling(kable(table$comparison_table[setdiff(1:13,5)], "latex", digit=2), latex_options = c("striped", "scale_down")), 
         file="Output/Images/TableRegSOC_comparison.png")

### 2020-10-06 ResultNotebooks/results_SOCmaps.Rmd
Mayor update of everything

rev       <- "rev0.7_mrSOC"
outputdir <- "Output/Images"

@@

SoilCarbon <- read.magpie("Data/SoilCarbon.rds")
Landuse    <- read.magpie("Data/Landuse.rds")

@@

cropland_dens    <- dimSums(SoilCarbon[,,"actualstate"][,,"crop"], dim=3)
cropland_dens[cropland_dens==0] <- NA

@@

library("ggplot2")
theme_set(theme_bw())
library("sf")
library("rnaturalearth")
library("rnaturalearthdata")
library(RColorBrewer)
library(sp)
library(rworldmap)
library(oce)

@@

SOCemis <- ggplot() + geom_line(data= as.data.frame(glo_SOCEmission[,seq(1975,2010,5),])[,c(3,6)],  aes(x = Year, y = Value, group=1)) +
  labs( x = "Year", 
        y = "Global cummulative \nSOC emission in GtC") +
  scale_x_discrete(breaks=seq(1965,2010,5)) +
  scale_y_continuous(limits=c(30,40), breaks=seq(30,40,5)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8))

@@

SOCshare <- ggplot(data = world) + geom_sf() + 
    geom_tile(data = subset(share2plot, Year=="2010", c("lon","lat","Value")), aes(x = lon, y = lat, fill = Value)) +
    scale_fill_stepsn(limits=c(0,2), colours = cols, 
                      name = expression("ratio of cropland SOC to potential natural SOC"), 
                      breaks=c(0.3,0.6,0.9,1.1,1.4,1.7,2),
                      labels=c("0     0.3","  0.6", "  0.9","  1.1","  1.4","  1.7","> 2"), na.value = "white",
                      guide = guide_legend(
                        title.theme=element_text(size=legend_size),
                        direction = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust = 0.5,
                        label.hjust = 1,
                        nrow = 1,
                        byrow = F,
                        label.position = "bottom",
                        keyheight = 0.5,
                        keywidth  = 2
                      )) +
    theme(legend.position="bottom",
          axis.title.x = element_blank(), 
          axis.title.y = element_blank(),
          legend.text=element_text(size=legend_size),
          rect=element_blank(),
          panel.background=element_rect(fill="#F8F8FF", size=c(0.7,0.7))
          )

@@

SOCincrease <- ggplot(data = world) + geom_sf() +
    geom_tile(data = subset(increase2plot, Year=="2010", c("lon","lat","Value")), aes(x = lon, y = lat, fill = Value)) +
    scale_fill_stepsn(limits=c(-100,100), colours = cols, 
                      name = expression("cropland SOC change in tons of carbon per hectar"), 
                      values=(c(-100,-50,-20,-10,10,20,50,100)+100)/200,
                      breaks=c(-50,-20,-10,10,20,50,100),
                      labels=c("> -100    -50", "  -20","  -10","  10","  20","  50"," > 100"), na.value = "white",
                      guide = guide_legend(
                        title.theme=element_text(size=legend_size),
                        direction = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust = 0.5,
                        label.hjust = 1,
                        nrow = 1,
                        byrow = F,
                        label.position = "bottom",
                        keyheight = 0.5,
                        keywidth  = 2
                      )) +
    theme(legend.position="bottom",
          axis.title.x = element_blank(), 
          axis.title.y = element_blank(),
          legend.text=element_text(size=legend_size),
          rect=element_blank(),
          panel.background=element_rect(fill="#F8F8FF", size=c(0.7,0.7))
          )

>>>>

rev       <- "rev0.76baseline"
outputdir <- "Output/Images"

@@

SoilCarbon <- read.magpie("Data/Baseline/SoilCarbon.rds")
Landuse    <- read.magpie("Data/Baseline/Landuse.rds")

@@

cropland_dens    <- dimSums(SoilCarbon[,,"actualstate"][,,"crop"], dim=3)
cropland_dens[Landuse[,,"crop"]==0] <- NA

@@

library("ggplot2")
theme_set(theme_bw())
library("sf")
library("rnaturalearth")
library("rnaturalearthdata")
library(RColorBrewer)
library(sp)
library(rworldmap)
library(oce) 
library(scales)

@@

squish_trans <- function(from, to, factor) {

  trans <- function(x) {
    if (any(is.na(x))) return(x)
    # get indices for the relevant regions
    isq <- x > from & x < to
    ito <- x >= to
    # apply transformation
    x[isq] <- from + (x[isq] - from)/factor
    x[ito] <- from + (to - from)/factor + (x[ito] - to)
    return(x)
  }

  inv <- function(x) {
    if (any(is.na(x))) return(x)
    # get indices for the relevant regions
    isq <- x > from & x < from + (to - from)/factor
    ito <- x >= from + (to - from)/factor
    # apply transformation
    x[isq] <- from + (x[isq] - from) * factor
    x[ito] <- to + (x[ito] - (from + (to - from)/factor))
    return(x)
  }
  # return the transformation
  return(trans_new("squished", trans, inv))
}

SOCemis <- ggplot() + geom_line(data= as.data.frame(-glo_SOCEmission[,seq(1975,2010,5),])[,c(3,6)],  aes(x = Year, y = Value, group=1)) +
  labs( x = "Year", 
        y = "Global SOC gap\n in GtC") +
  scale_x_discrete(breaks=seq(1975,2010,5)) +
  scale_y_continuous(trans = squish_trans(-35,0,15),
                     limits = c(-45,0),
                     breaks = c(0, -15, -35, -40, -45)) +
  theme(rect=element_blank(),
        axis.title.y= element_text(size=legend_size),
        axis.text.x = element_text(angle=60, hjust=0.8, vjust=0.8)) +
  annotate(geom="text", label="SOC debt", x=factor(1995), y=-35, size = 3) +
  annotate("segment", x = factor(1990), xend = factor(1990), y = 0, yend = -39, arrow=arrow(end="both", type="closed", length=unit(0.1, "inches")))

@@

SOCshare <- ggplot(data = world) + geom_sf() + 
    geom_tile(data = subset(share2plot, Year=="2010", c("lon","lat","Value")), aes(x = lon, y = lat, fill = Value)) +
    scale_fill_stepsn(limits=c(0,2), colours = cols, 
                      name = expression(" cropland SOC stock change factor (unitless)"), 
                      breaks=c(0.3,0.6,0.9,1.1,1.4,1.7,2),
                      labels=c("0     0.3","  0.6", "  0.9","  1.1","  1.4","  1.7","> 2"), na.value = "white",
                      guide = guide_legend(
                        title.theme=element_text(size=legend_size),
                        direction = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust = 0.5,
                        label.hjust = 1,
                        nrow = 1,
                        byrow = F,
                        label.position = "bottom",
                        keyheight = 0.5,
                        keywidth  = 2
                      )) +
    theme(legend.position="bottom",
          axis.title.x = element_blank(), 
          axis.title.y = element_blank(),
          legend.text=element_text(size=legend_size),
          rect=element_blank(),
          panel.background=element_rect(fill="#F8F8FF", size=c(0.7,0.7))
          )

@@

SOCincrease <- ggplot(data = world) + geom_sf() +
    geom_tile(data = subset(increase2plot, Year=="2010", c("lon","lat","Value")), aes(x = lon, y = lat, fill = Value)) +
    scale_fill_stepsn(limits=c(-100,100), colours = cols, 
                      name = expression("cropland SOC gap in tons of carbon per hectar"), 
                      values=(c(-100,-50,-20,-10,10,20,50,100)+100)/200,
                      breaks=c(-50,-20,-10,10,20,50,100),
                      labels=c("> -100    -50", "  -20","  -10","  10","  20","  50"," > 100"), na.value = "white",
                      guide = guide_legend(
                        title.theme=element_text(size=legend_size),
                        direction = "horizontal",
                        title.position = 'top',
                        # I shift the labels around, the should be placed 
                        # exactly at the right end of each legend key
                        title.hjust = 0.5,
                        label.hjust = 1,
                        nrow = 1,
                        byrow = F,
                        label.position = "bottom",
                        keyheight = 0.5,
                        keywidth  = 2
                      )) +
    theme(legend.position="bottom",
          axis.title.x = element_blank(), 
          axis.title.y = element_blank(),
          legend.text=element_text(size=legend_size),
          rect=element_blank(),
          panel.background=element_rect(fill="#F8F8FF", size=c(0.7,0.7))
          )

### 2020-10-06 ResultNotebooks/results_SOCtable.Rmd
Mayor update of everything

rev <- "rev0.6_mrSOC"

setConfig(cachefolder  = paste0("/home/kristine/mnt/rd3mod/inputdata/cache/", rev), forcecache = TRUE)
setConfig(sourcefolder = "/home/kristine/mnt/rd3mod/inputdata/sources/")
setConfig(outputfolder = "/home/kristine/mnt/rd3mod/inputdata/output/")
untar(paste0(getConfig("outputfolder"),"/",rev, "_h12_carbonbudget.tgz"), exdir="Data", extras="--keep-newer-files ")

SoilCarbon <- read.magpie("Data/SoilCarbon.rds")
Landuse    <- read.magpie("Data/Landuse.rds")

@@

SOCDens           <- dimSums(SoilCarbon[,,c("steadystate","actualstate","naturalstate")], dim=3.3) 
SOCDens[,,"naturalstate.crop"] <- SOCDens[,,"actualstate.crop"]

@@

steadystate_table  <- data.frame(dcast(as.data.frame(collapseNames(CShare_ipcczone[,findset("past"),"steadystate"])), 
                            Year ~ Data1, value.var="Value", row.names=findset("past")), row.names = "Year")

saveRDS(list(naturalstate_table = naturalstate_table,
             actualstate_table  = actualstate_table, 
             steadystate_table  = steadystate_table), "Output/SFC_climatezone.rds")

@@

CShare_ipcc <- new.magpie("GLO","y2010",outer(c("IPCC2006","IPCC2019"),unique(koepp2IPCC$ipcc_reduced), paste, sep="."))

CShare_ipcc[,,"IPCC2006.tropical_moist"]  <- "0.48"
CShare_ipcc[,,"IPCC2006.tropical_dry"]    <- "0.58-0.64" 
CShare_ipcc[,,"IPCC2006.temperate_moist"] <- "0.69"
CShare_ipcc[,,"IPCC2006.temperate_dry"]   <- "0.80"

CShare_ipcc[,,"IPCC2019.tropical_moist"]  <- "0.83"
CShare_ipcc[,,"IPCC2019.tropical_dry"]    <- "0.92" 
CShare_ipcc[,,"IPCC2019.temperate_moist"] <- "0.69-0.70"
CShare_ipcc[,,"IPCC2019.temperate_dry"]   <- "0.76-0.77"

comparison <- mbind(CShare_ipcc, 
                    round(add_dimension(collapseNames(CShare_ipcczone[,"y2010","naturalstate"]),
                                  add="SOCbudget",nm="model"),2))

print(dimOrder(comparison[,,sort(getNames(comparison,dim=1))], c(2,1)))

@@

>>>>

rev       <- "rev0.76baseline"
outputdir <- "Output/"

setConfig(cachefolder  = paste0("/home/kristine/mnt/rd3mod/inputdata/cache/", rev), forcecache = TRUE)
setConfig(sourcefolder = "/home/kristine/mnt/rd3mod/inputdata/sources/")
setConfig(outputfolder = "/home/kristine/mnt/rd3mod/inputdata/output/")
#untar(paste0(getConfig("outputfolder"),"/",rev, "_h12_carbonbudget.tgz"), exdir="Data/Baselin", extras="--keep-newer-files ")

SoilCarbon <- read.magpie("Data/Baseline/SoilCarbon.rds")
Landuse    <- read.magpie("Data/Baseline/Landuse.rds")

@@

SOCDens           <- dimSums(SoilCarbon[,,c("actualstate","naturalstate")], dim=3.3) 
SOCDens[,,"naturalstate.crop"] <- SOCDens[,,"actualstate.crop"]

@@

saveRDS(list(naturalstate_table = naturalstate_table,
             actualstate_table  = actualstate_table), paste0(outputdir, "SFC_climatezone.rds"))

@@

CShare_ipcc <- IShare_ipcc <- new.magpie("GLO","y2010",outer(c("IPCC2006","IPCC2019"),unique(koepp2IPCC$ipcc_reduced), paste, sep="."))

CShare_ipcc <- IShare_ipcc <- new.magpie("GLO","y2010",outer(c("IPCC2006","IPCC2019"),c("tropical_moist","tropical_dry","temperate_dry","temperate_moist"), paste, sep="."))

CShare_ipcc <- add_dimension(CShare_ipcc, dim=3.2, nm="default", add="subsystem")
IShare_ipcc <- add_dimension(IShare_ipcc, dim=3.2, nm="low_input", add="subsystem")

CShare_ipcc[,,"IPCC2006.default.tropical_moist"]  <- "0.48"
CShare_ipcc[,,"IPCC2006.default.tropical_dry"]    <- "0.58-0.64" 
CShare_ipcc[,,"IPCC2006.default.temperate_moist"] <- "0.69"
CShare_ipcc[,,"IPCC2006.default.temperate_dry"]   <- "0.80"

CShare_ipcc[,,"IPCC2019.default.tropical_moist"]  <- "0.83"
CShare_ipcc[,,"IPCC2019.default.tropical_dry"]    <- "0.92" 
CShare_ipcc[,,"IPCC2019.default.temperate_moist"] <- "0.69-0.70"
CShare_ipcc[,,"IPCC2019.default.temperate_dry"]   <- "0.76-0.77"

#Low input regime factor
IShare_ipcc[,,"IPCC2006.low_input.tropical_moist"]  <- "0.44"
IShare_ipcc[,,"IPCC2006.low_input.tropical_dry"]    <- "0.55-0.61" 
IShare_ipcc[,,"IPCC2006.low_input.temperate_moist"] <- "0.66"
IShare_ipcc[,,"IPCC2006.low_input.temperate_dry"]   <- "0.74"

IShare_ipcc[,,"IPCC2019.low_input.tropical_moist"]  <- "0.76"
IShare_ipcc[,,"IPCC2019.low_input.tropical_dry"]    <- "0.87" 
IShare_ipcc[,,"IPCC2019.low_input.temperate_moist"] <- "0.66-0.67"
IShare_ipcc[,,"IPCC2019.low_input.temperate_dry"]   <- "0.70-0.71"

getNames(CShare_ipcc) <- gsub("_", " ", getNames(CShare_ipcc))
getNames(IShare_ipcc) <- gsub("_", " ", getNames(IShare_ipcc))

comparison <- mbind(CShare_ipcc, IShare_ipcc,
                    round(add_dimension(setYears(collapseNames(CShare_ipcczone[,"y1990","naturalstate"]),"y2010"),
                                  nm="SOC budget.1990",add="model.year"),2),
                    round(add_dimension(collapseNames(CShare_ipcczone[,"y2010","naturalstate"]),
                                  nm="SOC budget.2010",add="model.year"),2))

#print(dimOrder(comparison[,,sort(getNames(comparison,dim=1))], c(2,1)))

comparison_table  <- data.frame(dcast(as.data.frame(collapseNames(comparison)), 
                           Data1 + Data2 ~ Data3, value.var="Value", 
                            row.names=levels(as.data.frame(comparison)$Data1)))

saveRDS(list(comparison_table = comparison_table), paste0(outputdir,"SFC_comparison.rds"))

@@

```{r kable2image}
library(kableExtra)

table <- readRDS("Output/SFC_comparison.rds")
colnames(table[[1]]) <- gsub("\\.", " ", colnames(table[[1]]))
colnames(table[[1]])[1] <- "Source"
colnames(table[[1]])[2] <- "Subsystem/Year"
save_kable(kable_styling(kable(table$comparison_table, "latex", digit=2), latex_options = c("striped", "scale_down")), 
         file="Output/Images/TableSCF_comparison.png")

table <- readRDS("Output/SFC_climatezone.rds")
colnames(table[[1]]) <- gsub("_", " ", colnames(table[[1]]))
colnames(table[[1]][1]) <- ""
as_image(kable_styling(kable(table$naturalstate_table[3:10,], "latex", digit=2), latex_options = c("striped", "scale_down")), 
         width=4, file="Output/Images/TableSCF_timeline.png")
```

### 2020-10-06 SOCbudgetPaper/SOCbudget.Rmd
Mayor update of everything

---
title: Management induced changes of soil organic carbon on global croplands 
journal: "`r rticles::copernicus_journal_abbreviations(journal_name = 'communication')`"
author:
  - given_name: Kristine
    surname: Karstens
    affiliation: 1
    email: kristine.karstens@pik-potsdam.de
    corresponding: true
  - given_name: Benjamin Leon
    surname: Bodirsky
    affiliation: 1
  - given_name: Your
    surname: Name
    affiliation: 2
  - given_name: Alexander
    surname: Popp
    affiliation: 1
affiliation:
  - code: 1
    address: Potsdam-Institut of Climate Impacts Research, Potsdam, Germany
  - code: 2
    address: Your affiliation 
abstract: |
  Soil organic carbon (SOC) is one of larges carbon stocks on earth. It is three times larger than the biospheric pool and more than twice as big as the athmospheric pool, when looking into the first meter of the earth soil profile. Human cropping activties led and still lead to a depletion of SOC though, which are so far not well represented in global assessments of historic carbon emissions. While SOC models often represent well the biochemical processes that lead to the accumulation and decay of SOC, the management decisions driving these biophysical processes are still little investigated on the global scale. Here we create a spatial explicit data set for agricutural management on cropland, especially for crop residue and manure management, based on global historic production (FAOSTAT), and land-use (LUH2) data; and combine it with the IPCC Tier 2 approach to create a half degree resolution SOC stock changes on mineral soils. We estimate that due to arable farming soils have lost over 37 GtOC of which 4 GtOC have been regained within the period 1975-2010. We show that, our results on global scale based on Tier 2 IPCC methodolgy are in good agreement with Tier 1 default assumptions. We also find that SOC is very sensitive to management decision such as residue recycling indicating the nessessity to incorporated better management data in soil models.
bibliography: SOCbudget.bib
running:
  title: R Markdown Template for Copernicus
  author: Nüst et al.
competinginterests: |
  The authors declare no competing interests.
# OPTIONAL:
algorithms: true
# See https://publications.copernicus.org/for_authors/licence_and_copyright.html, normally used for transferring the copyright, if needed.
copyrightstatement: |
  The author's copyright for this publication is transferred to institution/company.
availability:
  codedata: |
    Software code for paper and result prepartion can be found under www.github.com/k4rst3ns/. Data used for the output can be found under <something-with-zenodo>.  
authorcontribution: |
  Karstens wrote code and paper build on work of Bodirsky (and <here_could_be_your_names>). 
  Bodirsky, <here_could_be_your_names> and Popp revised paper.
disclaimer: |
  We like Copernicus.
acknowledgements: |
  Thanks to the rticles contributors!
output:
  bookdown::pdf_book:
    base_format: rticles::copernicus_article # for using bookdown features like \@ref()
    md_extensions: +raw_attribute
  md_document:
    variant: markdown_github
  rticles::copernicus_article: default
  bookdown::word_document2: default
  bookdown::pdf_document2: default
---
\newpage

>>>>

---
title: Management induced changes of soil organic carbon on global croplands 
journal: "`r rticles::copernicus_journal_abbreviations(journal_name = 'communication')`"
author:
  - given_name: Kristine
    surname: Karstens
    affiliation: 1
    email: kristine.karstens@pik-potsdam.de
    corresponding: true
  - given_name: Benjamin Leon
    surname: Bodirsky
    affiliation: 1
  - given_name: Your
    surname: Name
    affiliation: 2
  - given_name: Alexander
    surname: Popp
    affiliation: 1
affiliation:
  - code: 1
    address: Potsdam-Institut of Climate Impacts Research, Potsdam, Germany
  - code: 2
    address: Your affiliation 
abstract: |
  Soil organic carbon (SOC) is one of larges carbon stocks on earth. It is three times larger than the biospheric pool and more than twice as big as the athmospheric pool, when looking into the first meter of the earth soil profile. Human cropping activties led and still lead to a depletion of SOC though, which are so far not well represented in global assessments of historic carbon emissions. While SOC models often represent well the biochemical processes that lead to the accumulation and decay of SOC, the management decisions driving these biophysical processes are still little investigated on the global scale. Here we create a spatial explicit data set for agricutural management on cropland, especially for crop residue and manure management, based on global historic production (FAOSTAT), and land-use (LUH2) data; and combine it with the IPCC Tier 2 approach to create a half degree resolution SOC stock changes on mineral soils. We estimate that due to arable farming soils have lost over 37 GtOC of which 4 GtOC have been regained within the period 1975-2010. We show that, our results on global scale based on Tier 2 IPCC methodolgy are in good agreement with Tier 1 default assumptions. We also find that SOC is very sensitive to management decision such as residue recycling indicating the nessessity to incorporated better management data in soil models.
bibliography: SOCbudget.bib
running:
  title: R Markdown Template for Copernicus
  author: Nüst et al.
competinginterests: |
  The authors declare no competing interests.
# OPTIONAL:
algorithms: true
# See https://publications.copernicus.org/for_authors/licence_and_copyright.html, normally used for transferring the copyright, if needed.
copyrightstatement: |
  The author's copyright for this publication is transferred to institution/company.
availability:
  codedata: |
    Software code for paper and result prepartion can be found under www.github.com/k4rst3ns/. Data used for the output can be found under <something-with-zenodo>.  
authorcontribution: |
  Karstens wrote code and paper build on work of Bodirsky (and <here_could_be_your_names>). 
  Bodirsky, <here_could_be_your_names> and Popp revised paper.
disclaimer: |
  We like Copernicus.
acknowledgements: |
  Thanks to the rticles contributors!
output:
  rticles::copernicus_article: default
  md_document:
    variant: markdown_github
  bookdown::pdf_book:
    base_format: rticles::copernicus_article # for using bookdown features like \@ref()
    md_extensions: +raw_attribute
  bookdown::word_document2: default
  bookdown::pdf_document2: default
---
\newpage
